Visual Question Answering with DeepProbLog

### 2022-03-20 paper/paper.tex
Further review

The most important observation here is that the purely neural network approach overfits quickly and also achieves a considerably lower accuracy (68\% instead of almost 75\% for DeepProbLog). Another important remark is the fact that both approaches are clearly not longer able to attain 100\% accuracy. However, if the DeepProbLog network could train longer, it would be able to converge even further.

@@

DeepProbLog naturally will not make any `nonsense' mistakes such as answering `yes' to the question `What shape has the object under investigation?', since the possible correct answers are encoded in the program each time. However, the purely neural network based approach has remarkably learned to link the possible answers to the questions.

@@

Regarding the relational question: `How many objects have the same shape as the object under investigation?', a lot more confusion in both approaches is going on. DeepProbLog will typically be able to come close to the correct answer, but may make some `off-by-one' mistakes\footnote{I.e. one CNN that is mispredicting the shape of its object.}. The purely neural network based approach does a little worse in this perspective. It is also plausible that in this approach, the neural network may have observed that due to probabilistic reasons, there are likely three or four equal objects (inclusive the one under investigation), and hence prefer such an answer.

>>>>

The most important observation here is that the purely neural network approach overfits quickly and also achieves a considerably lower accuracy (68\% instead of almost 75\% for DeepProbLog). Another important remark is the fact that both approaches are clearly not longer able to attain 100\% accuracy. However, if the DeepProbLog network could train longer, it would be able to converge somewhat further.

@@

DeepProbLog naturally will not make any `nonsense' mistakes such as answering `yes' to the question `What shape has the object under investigation?', since the possible correct answers are encoded in the program. However, the purely neural network based approach has learned perfectly to link the possible answers to the questions.

@@

Regarding the relational question: `How many objects have the same shape as the object under investigation?', a lot more confusion in both approaches is going on. DeepProbLog will typically be able to come close to the correct answer, but may make some `off-by-one' mistakes\footnote{I.e. one CNN that is mispredicting the shape of its object.}. The purely neural network based approach does also in this perspective a little worse. It is also plausible that in this approach, the neural network may have observed that due to probabilistic reasons, there are likely three or four equal objects (inclusive the one under investigation), and hence prefers such an answer.
